Racets: Embedding Policy{-}Agnostic Programming in Racket

### 2018-07-20 paper/paper.tex
fix stuffs on Sec 3 semantics. Need to fix the format of Sec 3.

          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
                                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
                                     \fcol{(v_1 v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}

@@

@@

                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \and

@@

                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E v, \sigma''}

@@

                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\

@@

                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E v', \sigma'}

@@

                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\

@@

            \{+\ell, -\ell\} \cup pc = \varnothing \\\\

@@

          \inferrule[\textsc{Fac-Create-Left}]

@@

           e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}

@@

          \inferrule[\textsc{Fac-Create-Right}]

@@

           e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}

@@

      \end{array}
    \end{displaymath}
    \\
    \hfill \textit{(Label Creation / Observation)}
    \\
    \[
    \begin{array}{cc}
      {\color{\colorFAC}
        \inferrule[\textsc{Let-Label}]
          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \langle \lambda x. ~ e, \rho' \rangle \\\\
           \alpha \not\in dom(\sigma') \and \sigma'' = \sigma' [\alpha \mapsto \langle \lambda x. ~ e, \rho' \rangle] \\\\
           e_2, \rho [ \ell \mapsto \alpha ], \sigma'' \Downarrow_{pc}^E \sigma''', v}
          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
          & 
          {\color{\colorFAC}
          \inferrule[\textsc{Obs}]
                    {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell
                      \and e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v  \\\\
                      \langle (\lambda x.~e), \rho' \rangle = \sigma''(\ell) \\\\
                      e, \rho' [x \mapsto v], \sigma'' \Downarrow_{pc}^E \sigma''', v^{\pm} \\\\
                      e_3, \rho, \sigma''' \Downarrow_{pc}^E \sigma'''', v' \\\\
                      v'' = \fcol{\var{obs}(\ell, pc, v', v^{\pm})}}
                    {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'''', v''}}
    \end{array}
    \]
    \\
    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
    \\
    \begingroup
    \color{\colorMATH}
    \begin{displaymath}
      \begin{array}{c}
        \begin{array}{ccc}
          {\color{\colorMATH}
          \inferrule[\textsc{App-$\star$}]
          { }
          {(\star ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, \star}}
          & 
          {\color{\colorMATH}
          \inferrule[\textsc{App-Base}]
          {e, \rho'[x \mapsto v], \sigma \Downarrow_{pc}^E \sigma', v' }
          {(\langle \lambda x.~e, \rho' \rangle ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
          & 
          {\color{\colorFAC}
          \inferrule[\textsc{App-Split}]
          {\{+\ell, -\ell\} \cap pc = \varnothing \and
            (v^+ ~ v), \rho, \sigma \Downarrow_{pc \cup \{+\ell\}}^A \sigma', {v^+}' \\\\
            (v^- ~ v), \rho, \sigma' \Downarrow_{pc \cup \{-\ell\}}^A \sigma'', {v^-}' \and
            v' = \formfacet{\{+ \ell\}}{{v^+}'}{{v^-}'}}
          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma'', v'}}
        \end{array}
        \\
        \begin{array}{cc}
          {\color{\colorFAC}
          \inferrule[\textsc{App-Facet-Pos}]
          {+\ell \in pc \\\\
            (v^+ ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}
          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
          & 
          {\color{\colorFAC}
          \inferrule[\textsc{App-Facet-Neg}]
          {-\ell \in pc \\\\
            (v^- ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}
          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
        \end{array}
      \end{array}
    \end{displaymath}
              %%\inferrule[]
    \endgroup
    \label{fig:semantics}
\end{figure*}

>>>>

          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v_1 \and
                                     e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v_2 \\\\
                                     \fcol{(v_1 ~ v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}

@@

        \\\\

@@

                    {e, \rho, \sigma \Downarrow_{pc}^E \sigma', v \and

@@

                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E \sigma'', \alpha}

@@

                    {e, \rho, \sigma \Downarrow_{pc}^E \sigma', v \\\\

@@

                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E \sigma', v'}

@@

                    {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v_1 \and
                     e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v_2 \\\\

@@

            \{+\ell, -\ell\} \cap pc = \varnothing \\\\

@@

          \inferrule[\textsc{Fac-Create-Pos}]

@@

           e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v}

@@

          \inferrule[\textsc{Fac-Create-Neg}]

@@

           e_3, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v}

@@

    \hfill \textit{(Label Creation / Observation)}
    \[
    \begin{array}{cc}
        \inferrule[\textsc{Let-Label}]
          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \langle \lambda x. ~ e, \rho' \rangle \\\\
           \alpha \not\in dom(\sigma') \and \sigma'' = \sigma' [\alpha \mapsto \langle \lambda x. ~ e, \rho' \rangle] \\\\
           e_2, \rho [ \ell \mapsto \alpha ], \sigma'' \Downarrow_{pc}^E \sigma''', v}
          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
          \inferrule[\textsc{Obs}]
                    {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell
                      \and e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v  \\\\
                      \langle (\lambda x.~e), \rho' \rangle = \sigma''(\ell) \\\\
                      e, \rho' [x \mapsto v], \sigma'' \Downarrow_{pc}^E \sigma''', v^{\pm} \\\\
                      e_3, \rho, \sigma''' \Downarrow_{pc}^E \sigma'''', v' \\\\
                      v'' = \fcol{\var{obs}(\ell, v', v^{\pm})}}
                    {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'''', v''}}
    \]
    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v_1 ~ v_2), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
          {\color{\colorMATH}
          \inferrule[\textsc{App-$\star$}]
          { }
          {(\star ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, \star}}
          {\color{\colorMATH}
          \inferrule[\textsc{App-Base}]
          {e, \rho'[x \mapsto v], \sigma \Downarrow_{pc}^E \sigma', v' }
          {(\langle \lambda x.~e, \rho' \rangle ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
          \inferrule[\textsc{App-Split}]
          {\{+\ell, -\ell\} \cap pc = \varnothing \and
            (v^+ ~ v), \rho, \sigma \Downarrow_{pc \cup \{+\ell\}}^A \sigma', {v^+}' \\\\
            (v^- ~ v), \rho, \sigma' \Downarrow_{pc \cup \{-\ell\}}^A \sigma'', {v^-}' \and
            v' = \formfacet{\{+ \ell\}}{{v^+}'}{{v^-}'}}
          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma'', v'}}
        \begin{array}{cc}
        \\\\
          \inferrule[\textsc{App-Facet-Pos}]
          {+\ell \in pc \\\\
            (v^+ ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}
          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
          \inferrule[\textsc{App-Facet-Neg}]
          {-\ell \in pc \\\\
            (v^- ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}
          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
    \newpage
    \hfill \textit{(Metafunctions)}
      \begin{array}{rclrr}
        {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
        {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
        {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
        {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
      \begin{array}{rclrr}
        {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
        {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
        & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
      \begin{array}{rclrr}
        {obs(\ell, b, bv)} & {=} & {bv} & & \\
        {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
        {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
        {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
              %%\inferrule[]
    \label{fig:semantics}
\end{figure*}
